Examining background gene list issue in clusterProfiler - RNA-seq example

### 2024-09-05 analysis/analyse_rnaseq1.Rmd
get set len

>>>>

## Characterise sets specific to original and uncorrected analysis

```{r,spec}

compare_ora2 <- function(bad,good){
  badup <- bad$orabad_up
  baddn <- bad$orabad_dn
  goodup <- good$oragood_up
  gooddn <- good$oragood_dn
  mup <- merge(badup,goodup,by=0)
  mdn <- merge(baddn,gooddn,by=0)
  bup <- subset(mup,p.adjust.x<0.05)$Row.names
  gup <- subset(mup,p.adjust.y<0.05)$Row.names
  bdn <- subset(mdn,p.adjust.x<0.05)$Row.names
  gdn <- subset(mdn,p.adjust.y<0.05)$Row.names
  sig_bad <- unique(c(bup,bdn))
  sig_good <- unique(c(gup,gdn))
  itx <- intersect(sig_bad,sig_good)
  spec_good <- setdiff(sig_good,sig_bad)
  result=list("intersect"=itx,"spec_good"=spec_good)
  return(result)
}

ora_dat3 <- mclapply(1:nrow(params), function(i) {
  j=params[i,1]
  k=params[i,2]
  bad <- orabad(d[[j]],gs[[k]])
  good <- oragood(d[[j]],gs[[k]])
  res <- compare_ora2(bad,good)
  return(res)
} , mc.cores=8)

gslengths <- unlist(lapply(gs,function(x) { lapply(x,length) } ) )
names(gslengths) <- sapply((strsplit(names(gslengths),"\\.")),"[[",2)

speclen <- lapply(ora_dat3, function(j) {
  itxlen <- mean(gslengths[which(names(gslengths) %in% j[[1]])])
  speclen <- mean(gslengths[which(names(gslengths) %in% j[[2]])])
  return(c("itxlen"=itxlen,"spec"=speclen))
})

itxlenmx <- matrix(sapply(speclen,"[[",1),nrow=7)
speclenmx <- matrix(sapply(speclen,"[[",2),nrow=7)

colMeans(itxlenmx,na.rm=TRUE) / colMeans(speclenmx,na.rm=TRUE)

mean( ( colMeans(speclenmx,na.rm=TRUE) - colMeans(itxlenmx,na.rm=TRUE) ) / colMeans(itxlenmx,na.rm=TRUE) )

Overall, the size of gene sets specific to the "fixed" analysis were 9.3% smaller than
the intersect.
